---
title       : Like my Random Forest Shiny App!
subtitle    : Or else...
author      : Ryan Greenway
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Random Forest Shiny Application

You can find my application at
https://greenway1.shinyapps.io/DataProducts

What it does: Allows you to determine how much better your
predictions will get with varying samples and more trees in the model


1. RUN SIMULATIONS!
 
2. Machine Learning!
 
 The <span style="color:blue; font-weight:bold">future</span> is near...

--- .class #id 

## RandomForest Code

The main code for the Random Forest algorithm:
```{r}
  library(caret); library(randomForest); library(AppliedPredictiveModeling);
  data(segmentationOriginal); set.seed(32324);
    
    inTrain <- createDataPartition(y=segmentationOriginal$Class,p=0.6,list=FALSE)
    training <- segmentationOriginal[inTrain,]; testing <- segmentationOriginal[-inTrain,];
    fit <- randomForest(Class ~ ., data=training, importance=TRUE, ntree=20)
```

---

## Results of Machine Learning

An example of the output:
```{r, echo=FALSE}
    print(fit)
```

---

## Conclusion

How this compares with our holdout sample:

```{r}
    predTest <- predict(fit,testing)
    table(predTest,testing$Class)
```

That's it!  In shiny you can adjust the sample size from 10% to 90%
and also the number of trees from 10 to 500. <span style="color:red; font-weight:bold">Enjoy!</span>
